Web Scraping

### 2022-03-03 manuscript_version/manuscript_metapsych.Rmd
update for tables why do they hate me

```{r load_packages, include = FALSE}
library(papaja) 
library(MuMIn)
library(reshape)
library(nlme)
library(ggplot2)
library(expss)
library(MOTE)
library(quanteda)
library(quanteda.textstats)
library(tm)
library(ngram)
library(ggplot2)
library(reshape)

@@

```{r scraping, eval=FALSE, include=FALSE}

library(rvest)
####NY Times####
#Specifying the url for desired website to be scrapped
url <- 'https://www.nytimes.com/section/politics'

#Reading the HTML code from the website - headlines
webpage <- read_html(url)
headline_data = html_nodes(webpage,'.story-link a, .story-body a')

attr_data = html_attrs(headline_data) 
attr_data

urlslist = unlist(attr_data)
urlslist = urlslist[grep("http", urlslist)]
urlslist = unique(urlslist)
urlslist

##start a data frame
NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
colnames(NYtimesDF) = c("Source", "Url", "Text")
NYtimesDF = as.data.frame(NYtimesDF)

##for loops
for (i in 1:length(urlslist)){

  ##read in the URL
  webpage <- read_html(urlslist[i])

  ##pull the specific nodes
  headline_data = html_nodes(webpage,'.story-content')

  ##pull the text
  text_data = html_text(headline_data)

  ##save the data
  NYtimesDF$Source[i] = "NY Times"
  NYtimesDF$Url[i] = urlslist[i]
  NYtimesDF$Text[i] = paste(text_data, collapse = "")
    } ##end for loop

####NPR original front page####
url2 = 'https://www.npr.org/sections/politics/'
webpage2 = read_html(url2)
headline_data2 = html_nodes(webpage2,'.title a')

#URLs
attr_data2 = html_attrs(headline_data2) 
attr_data2

urlslist2 = unlist(attr_data2)
urlslist2 = urlslist2[grep("http", urlslist2)]
urlslist2

##start a data frame
NPRDF = matrix(NA, nrow = length(urlslist2), ncol = 3)
colnames(NPRDF) = c("Source", "Url", "Text")
NPRDF = as.data.frame(NPRDF)

##for loops
for (i in 1:length(urlslist2)){

  ##read in the URL
  webpage2 <- read_html(urlslist2[i])

  ##pull the specific nodes
  headline_data2 = html_nodes(webpage2,'#storytext > p')

  ##pull the text
  text_data2 = html_text(headline_data2)

  ##save the data
  NPRDF$Source[i] = "NPR"
  NPRDF$Url[i] = urlslist2[i]
  NPRDF$Text[i] = paste(text_data2, collapse = "")
} ##end for loop

####Fox News####
url3 = 'http://www.foxnews.com/politics.html'
url3.1 = 'http://www.foxnews.com/category/politics/executive.html'
url3.2 = 'http://www.foxnews.com/category/politics/senate.htm.html'
url3.3 = 'http://www.foxnews.com/category/politics/house-representatives.html'
url3.4 = 'http://www.foxnews.com/category/politics/judiciary.html'
url3.5 = 'http://www.foxnews.com/category/politics/foreign-policy.html'
url3.6 = 'http://www.foxnews.com/category/politics/elections.html'
webpage3 = read_html(url3)
webpage3.1 = read_html(url3.1)
webpage3.2 = read_html(url3.2)
webpage3.3 = read_html(url3.3)
webpage3.4 = read_html(url3.4)
webpage3.5 = read_html(url3.5)
webpage3.6 = read_html(url3.6)

headline_data3 = html_nodes(webpage3, '.story- a , .article-list .title a')
headline_data3.1 = html_nodes(webpage3.1, '.story- a , .article-list .title a')
headline_data3.2 = html_nodes(webpage3.2, '.story- a , .article-list .title a')
headline_data3.3 = html_nodes(webpage3.3, '.story- a , .article-list .title a')
headline_data3.4 = html_nodes(webpage3.4, '.story- a , .article-list .title a')
headline_data3.5 = html_nodes(webpage3.5, '.story- a , .article-list .title a')
headline_data3.6 = html_nodes(webpage3.6, '.story- a , .article-list .title a')

#headline_data = html_text(headline_data)
head(headline_data3)

attr_data3 = html_attrs(headline_data3) 
attr_data3.1 = html_attrs(headline_data3.1) 
attr_data3.2 = html_attrs(headline_data3.2) 
attr_data3.3 = html_attrs(headline_data3.3) 
attr_data3.4 = html_attrs(headline_data3.4) 
attr_data3.5 = html_attrs(headline_data3.5) 
attr_data3.6 = html_attrs(headline_data3.6)

attr_data3

urlslist3 = c(unlist(attr_data3), unlist(attr_data3.1), 
              unlist(attr_data3.2), unlist(attr_data3.3), 
              unlist(attr_data3.4), unlist(attr_data3.5, attr_data3.6))
##find all that are href
urlslist3 = urlslist3[grep("http|.html", urlslist3)]
##fix the ones without the leading foxnews.com
urlslist3F = paste("http://www.foxnews.com", urlslist3[grep("^http", urlslist3, invert = T)], sep = "")
urlslist3N = urlslist3[grep("^http", urlslist3)]
urlslist3 = c(urlslist3N, urlslist3F)
urlslist3 = unique(urlslist3)
urlslist3

##start a data frame
FoxDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
colnames(FoxDF) = c("Source", "Url", "Text")
FoxDF = as.data.frame(FoxDF)

##for loops
for (i in 1:length(urlslist3)){

  ##read in the URL
  webpage3 <- read_html(urlslist3[i])

  ##pull the specific nodes
  headline_data3 = html_nodes(webpage3,'p+ p , .fn-video+ p , .twitter+ p , .speakable')

  ##pull the text
  text_data3 = html_text(headline_data3)

  ##save the data
  FoxDF$Source[i] = "Fox News"
  FoxDF$Url[i] = urlslist3[i]
  FoxDF$Text[i] = paste(text_data3, collapse = "")
} ##end for loop

####Breitbart####
url4 = 'http://www.breitbart.com/big-government/'
webpage4 = read_html(url4)
headline_data4 = html_nodes(webpage4, '.title a , #grid-block-0 span , #BBTrendUL a , #disqus-popularUL a , font')
#headline_data4 = html_text(headline_data4)
head(headline_data4)

attr_data4 = html_attrs(headline_data4) 
attr_data4

urlslist4 = unlist(attr_data4)
##find all that are href
urlslist4 = urlslist4[grep("http|/big-government", urlslist4)]
##fix the ones without the leading bb
urlslist4F = paste("http://www.breitbart.com", urlslist4[grep("^http", urlslist4, invert = T)], sep = "")
urlslist4N = urlslist4[grep("^http", urlslist4)]
urlslist4 = c(urlslist4N, urlslist4F)
urlslist4 = unique(urlslist4)
urlslist4

##start a data frame
BreitbartDF = matrix(NA, nrow = length(urlslist4), ncol = 3)
colnames(BreitbartDF) = c("Source", "Url", "Text")
BreitbartDF = as.data.frame(BreitbartDF)

##for loops
for (i in 1:length(urlslist4)){

  ##read in the URL
  webpage4 <- read_html(urlslist4[i])

  ##pull the specific nodes
  headline_data4 = html_nodes(webpage4,'.entry-content p , h2')

  ##pull the text
  text_data4 = html_text(headline_data4)

  ##save the data
  BreitbartDF$Source[i] = "Breitbart"
  BreitbartDF$Url[i] = urlslist4[i]
  BreitbartDF$Text[i] = paste(text_data4, collapse = "")
} ##end for loop

####NPR Archive####
url5 = 'https://www.npr.org/sections/politics/archive'
webpage5 = read_html(url5)
headline_data5 = html_nodes(webpage5,'.title a')
#headline_data = html_text(headline_data)
#head(headline_data)

#URLs
attr_data5 = html_attrs(headline_data5) 
attr_data5

urlslist5 = unlist(attr_data5)
urlslist5 = urlslist5[grep("http", urlslist5)]
urlslist5

##start a data frame
NPRArchiveDF = matrix(NA, nrow = length(urlslist5), ncol = 3)
colnames(NPRArchiveDF) = c("Source", "Url", "Text")
NPRArchiveDF = as.data.frame(NPRArchiveDF)

##for loops
for (i in 1:length(urlslist5)){

  ##read in the URL
  webpage5 <- read_html(urlslist5[i])

  ##pull the specific nodes
  headline_data5 = html_nodes(webpage5,'#storytext > p')

  ##pull the text
  text_data5 = html_text(headline_data5)

  ##save the data
  NPRArchiveDF$Source[i] = "NPR"
  NPRArchiveDF$Url[i] = urlslist5[i]
  NPRArchiveDF$Text[i] = paste(text_data5, collapse = "")
} ##end for loop

####put together####
##set your working directory
setwd("~/OneDrive - Missouri State University/RESEARCH/2 projects/Will-Pilot")

##import the overalldata 
overalldata = read.csv("../exp1_data/overalldata.csv")

##combine with new data (add the other DF names in here...)
newdata = rbind(overalldata, NYtimesDF, NPRDF, FoxDF, BreitbartDF, NPRArchiveDF)

#temp NPR updates
#newdata = newdata[ , -4]
#newdata = rbind(newdata, NPRArchiveDF)

#change politics archive to NPR, so we can eliminate dupes
#newdata$Source[newdata$Source == "NPR Politics Archive"] = "NPR"
#newdata$Source = droplevels(newdata$Source)

##make the newdata unique in case of overlap across days
newdata = unique(newdata)

##write it back out
#write.csv(newdata, "overalldata.csv", row.names = F)

##number of articles
table(newdata$Source)

##number of words
library(ngram)
newdata$Text = as.character(newdata$Text)
for (i in 1:nrow(newdata)) {

  #newdata$writing[i] = preprocess(newdata$Text[i], case="lower", remove.punct=TRUE)
  newdata$wordcount[i] = string.summary(newdata$Text[i])$words

tapply(newdata$wordcount, newdata$Source, mean)
tapply(newdata$wordcount, newdata$Source, sum)

@@

```{r data-cleanup, eval=FALSE, include=FALSE}
##pull in the data
master = read.csv("../exp1_data/overalldata.csv", stringsAsFactors = F)

for (i in 1:nrow(master)) {
  master$wordcount[i] = wordcount(master$Text[i])
}

nozero = subset(master, wordcount > 0)
tapply(nozero$wordcount, nozero$Source, mean)
tapply(nozero$wordcount, nozero$Source, sum)

##take out the disqus ones
nodis = nozero[ -c(grep("disqus", nozero$Url)), ]

##figure out the duplicates
nodis$URLS = duplicated(nodis$Url)

##all data
final = subset(nodis, URLS == FALSE)

tapply(final$wordcount, final$Source, mean)
tapply(final$wordcount, final$Source, sum)

write.csv(final, "finaldata.csv")

@@

```{r stem_text, eval=TRUE, include=FALSE}

final = read.csv("../exp1_data/finaldata.csv", stringsAsFactors = F)
final = na.omit(final) #one weird NA line

@@

```{r exp1-source-descriptives, results = 'asis', echo = FALSE, message = F}

final$uniquewords = NA
final$valenceavg = NA

@@

tableprint = tableprint[c(3, 4, 1, 2) , ]

#change this to match
apa_table(as.data.frame(tableprint),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula. V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
          caption = "Experiment 1 - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 6)), 
          font_size = 'footnotesize',
          placement = 'pt'
          )
```

@@

```{r exp1-table, results = 'asis', echo = F}
#MFD, mean, sd, mean, sd, t, p, d
tableprint = matrix(NA, ncol = 8, nrow = 5)
colnames(tableprint) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")

@@

#put in the numbers
tableprint[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                    harm_d$d)
tableprint[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1, 
                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
                    fair_d$d)
tableprint[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1, 
                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
                    ingroup_d$d)
tableprint[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1, 
                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
                    authority_d$d)
tableprint[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1, 
                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
                    purity_d$d)

tableprint[ , c(2:6, 8)] = printnum(as.numeric(tableprint[ , c(2:6, 8)]))
tableprint[ , 7] = printp(as.numeric(tableprint[ , 7]))

apa_table(tableprint,
          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
          caption = "Experiment 1 Results - Multilevel Model", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7)),
          font_size = 'footnotesize',
          placement = 'pt'
          )
```

@@

```{r NYTimes_kav, eval = F, include = F}

library(rvest)
library(RSelenium)

rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#page for NYTIMES
url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'

#navigate to it
remDr$navigate(url)

#click the button 
#don't change class name
#right click --> inspect element 
webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")

#with 752 results at 10 per page we need
#752 - 10 original = 742 / 10 per click = 75 clicks

for (i in 1:75) { #change this to 75 later
  webElem$clickElement()
  Sys.sleep(runif(1, 1, 5))
}

webpage <-remDr$getPageSource()

#Reading the HTML code from the website - headlines
webpage2 <- read_html(unlist(webpage))

headline_data = html_nodes(webpage2,'a')

attr_data = html_attrs(headline_data) 
attr_data

urlslist = unlist(attr_data)
urlslist = urlslist[grep(".html", urlslist)]
urlslist = urlslist[grep("/2018", urlslist)]
urlslist = unique(urlslist)
urlslist

#paste NY on front
urlslist = paste("https://www.nytimes.com", urlslist, sep = "")

##start a data frame
NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
colnames(NYtimesDF) = c("Source", "Url", "Text")
NYtimesDF = as.data.frame(NYtimesDF)

##for loops
for (i in 1:length(urlslist)){

  ##read in the URL
  webpage <- read_html(urlslist[i])

  ##pull the specific nodes
  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')

  ##pull the text
  text_data = html_text(headline_data)

  ##save the data
  NYtimesDF$Source[i] = "NY Times"
  NYtimesDF$Url[i] = urlslist[i]
  NYtimesDF$Text[i] = paste(text_data, collapse = "")
  Sys.sleep(runif(1, 1, 10)) #don't make them angry
} ##end for loop

write.csv(NYtimesDF, "NYtimes_kav.csv", row.names = F)

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

```{r NYTimes_shut, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#page for NYTIMES
url <- 'https://www.nytimes.com/search?endDate=20190208&query=government%20shutdown&sort=best&startDate=20181208'

#navigate to it
remDr$navigate(url)

#click the button 
#don't change class name
#right click --> inspect element 
webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")

#with 803 results at 10 per page we need
#803 - 10 original / 10 per click is 80 clicks

for (i in 1:80) {
  webElem$clickElement()
  Sys.sleep(runif(1, 1, 5))
}

webpage <-remDr$getPageSource()

#Reading the HTML code from the website - headlines
webpage2 <- read_html(unlist(webpage))

headline_data = html_nodes(webpage2,'a')

attr_data = html_attrs(headline_data) 
#attr_data

urlslist = unlist(attr_data)
urlslist = urlslist[grep(".html", urlslist)]
urlslist = urlslist[grep("/201", urlslist)]
urlslist = unique(urlslist)
urlslist

#paste NY on front
urlslist = paste("https://www.nytimes.com", urlslist, sep = "")

##start a data frame
NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
colnames(NYtimesDF) = c("Source", "Url", "Text")
NYtimesDF = as.data.frame(NYtimesDF)

##for loops
for (i in 1:length(urlslist)){

  ##read in the URL
  webpage <- read_html(urlslist[i])

  ##pull the specific nodes
  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')

  ##pull the text
  text_data = html_text(headline_data)

  ##save the data
  NYtimesDF$Source[i] = "NY Times"
  NYtimesDF$Url[i] = urlslist[i]
  NYtimesDF$Text[i] = paste(text_data, collapse = "")
  Sys.sleep(runif(1, 1, 10)) #don't make them angry
} ##end for loop

write.csv(NYtimesDF, "NYtimes_gs.csv", row.names = F)
beep(sound = 5)

remDr$close()
# stop the selenium server
rD[["server"]]$stop()
```

```{r NPR_kav, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#create a blank space to put the links
urlslist_final = list()

##loop through the page number at the end until done with ~1000 / 20 = 50
for (i in 1:50) { ##change this to 50

  url = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)

  #navigate to it
  remDr$navigate(url)

  #scroll on the page
  webscroll <- remDr$findElement("css", "body")
  webscroll$sendKeysToElement(list(key = "end"))

  #get the links
  webElems <- remDr$findElements(using = "css", "[href]")
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))

} #close the loop

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

beep(sound = 3)

urlslist = unlist(urlslist_final)
#find all the ones with /2018/
urlslist2 = urlslist[grep("/2018", urlslist)]
urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
urlslist2 = unique(urlslist2)
temp = strsplit(urlslist2, split = "/")
temp2 = plyr::ldply(temp, rbind)
temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)

#deal with the ones with extra parts
temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]

#pull only the right dates
rows = rownames(temp2[ temp2$`4` == 2018 & #must be 2018 and 
                         (temp2$`5` == "09" & as.numeric(temp2$`6`)>=13 | 
                            temp2$`5` == "10" & as.numeric(temp2$`6`)<=11), #Must be 9 or 10 
                ])

urlslist3 = urlslist2[as.numeric(rows)]

##start a data frame
NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
colnames(NPRDF) = c("Source", "Url", "Text")
NPRDF = as.data.frame(NPRDF)

##for loops
for (i in 1:length(urlslist3)){

  ##read in the URL
  webpage2 <- read_html(urlslist3[i])

  ##pull the specific nodes
  headline_data2 = html_nodes(webpage2,'#storytext > p')

  ##pull the text
  text_data2 = html_text(headline_data2)

  ##save the data
  NPRDF$Source[i] = "NPR"
  NPRDF$Url[i] = urlslist3[i]
  NPRDF$Text[i] = paste(text_data2, collapse = "")
  Sys.sleep(runif(1, 1, 10))
} ##end for loop

beep(sound = 3)

write.csv(NPRDF, "NPR_kav.csv", row.names = F)

```{r NPR_shut, eval = F, include = F}

library(rvest)
library(RSelenium)
library(beepr)

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#create a blank space to put the links
urlslist_final = list()

##loop through the page number at the end until done with ~3316 / 20 = 166
for (i in 1:166) {

  url = paste0('https://www.npr.org/search?query=government%20shutodwn&page=', i)

  #navigate to it
  remDr$navigate(url)

  #scroll on the page
  webscroll <- remDr$findElement("css", "body")
  webscroll$sendKeysToElement(list(key = "end"))

  #get the links
  webElems <- remDr$findElements(using = "css", "[href]")
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))

} #close the loop

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

beep(sound = 3)

urlslist = unlist(urlslist_final)
#find all the ones with /2018/
urlslist2 = urlslist[grep("/201", urlslist)]
urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
urlslist2 = unique(urlslist2)
temp = strsplit(urlslist2, split = "/")
temp2 = plyr::ldply(temp, rbind)
temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)

#deal with the ones with extra parts
temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]

#pull only the right dates
rows = rownames(temp2[ (temp2$`4` == 2018 | temp2$`4` == 2019) & #must be 2018/19 and  
                         (
                           (temp2$`5` == "12" & as.numeric(temp2$`6`)>8 & temp2$`4` == 2018) | #after dec 12
                            (temp2$`5`== "01" & temp2$`4` == 2019) | #all of jan
                            (temp2$`5` == "02" & as.numeric(temp2$`6`)<8 & temp2$`4` == 2019)
                           ), #before feb 8
                ])

urlslist3 = urlslist2[as.numeric(rows)]

##start a data frame
NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
colnames(NPRDF) = c("Source", "Url", "Text")
NPRDF = as.data.frame(NPRDF)

##for loops
for (i in 315:length(urlslist3)){

  ##read in the URL
  webpage2 <- read_html(urlslist3[i])

  ##pull the specific nodes
  headline_data2 = html_nodes(webpage2,'#storytext > p')

  ##pull the text
  text_data2 = html_text(headline_data2)

  ##save the data
  NPRDF$Source[i] = "NPR"
  NPRDF$Url[i] = urlslist3[i]
  NPRDF$Text[i] = paste(text_data2, collapse = "")
  Sys.sleep(runif(1, 1, 10))
} ##end for loop

beep(sound = 3)

write.csv(NPRDF, "NPR_gs.csv", row.names = F)
```

```{r Slate_kav, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

url = "https://slate.com/search?q=kavanaugh&via=homepage_nav_search"

remDr$navigate(url)

#create a blank space to put the links
urlslist_final = list()

#loop over the results and go through them
#appear to be 10 pages
for (i in 1:10){

  #find the button to click on 
  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")

  #don't go too fast for the page to load
  Sys.sleep(runif(1, 1, 5))

  #click on the page number
  webClick[[i]]$clickElement()

  #page reload
  Sys.sleep(runif(1, 1, 5))

  #find the urls for page X
  webElems <- remDr$findElements(using = "css", "[href]")

  #add the urls to a list
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))
}

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

beep(sound = 3)

##deal with the URLS
urlslist = unlist(urlslist_final)

#find all the ones with /2018/
urlslist2 = urlslist[grep("/2018/10|/2018/09", urlslist)]
urlslist2 = unique(urlslist2)

#71 articles seems suspiciously low, so also scraped this page
#https://slate.com/tag/brett-kavanaugh/

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#create a blank space to put the links
urlslist_final = list()

#loop over the results and go through them
#337 / 20 = 17 pages
for (i in 1:17){

  url = paste0("https://slate.com/tag/brett-kavanaugh/", i)

  remDr$navigate(url)

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))

  #find the urls for page X
  webElems <- remDr$findElements(using = "css", "[href]")

  #add the urls to a list
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))
}

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

beep(sound = 3)

##deal with the URLS
urlslist = unlist(urlslist_final)

#find all the ones with /2018/
urlslist2.1 = urlslist[grep("/2018/10|/2018/09", urlslist)]
urlslist2.1 = unique(urlslist2.1)

urlslist3 = unique(c(urlslist2, urlslist2.1))

##start a data frame
SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
colnames(SLATEDF) = c("Source", "Url", "Text")
SLATEDF = as.data.frame(SLATEDF)

##for loops
for (i in 1:length(urlslist3)){

  ##read in the URL
  webpage2 <- read_html(urlslist3[i])

  ##pull the specific nodes
  headline_data2 = html_nodes(webpage2,'.slate-paragraph')

  ##pull the text
  text_data2 = html_text(headline_data2)

  ##save the data
  SLATEDF$Source[i] = "SLATE"
  SLATEDF$Url[i] = urlslist3[i]
  SLATEDF$Text[i] = paste(text_data2, collapse = "")
  Sys.sleep(runif(1, 1, 10))
} ##end for loop

beep(sound = 3)

write.csv(SLATEDF, "SLATE_kav.csv", row.names = F)

```{r SLATE_shut, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

url = "https://slate.com/search?q=government+shutdown"

remDr$navigate(url)

#create a blank space to put the links
urlslist_final = list()

#loop over the results and go through them
#appear to be 10 pages
for (i in 1:10){

  #find the button to click on 
  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")

  #don't go too fast for the page to load
  Sys.sleep(runif(1, 1, 5))

  #click on the page number
  webClick[[i]]$clickElement()

  #page reload
  Sys.sleep(runif(1, 1, 5))

  #find the urls for page X
  webElems <- remDr$findElements(using = "css", "[href]")

  #add the urls to a list
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))
}

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

beep(sound = 3)

##deal with the URLS
urlslist = unlist(urlslist_final)

#find all the ones from 12 2018 to 02 2019
urlslist2 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
urlslist2 = unique(urlslist2)

#60 something articles seems suspiciously low, so also scraped this page
#https://slate.com/tag/governtment-shutdown

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

#create a blank space to put the links
urlslist_final = list()

#loop over the results and go through them
#354 / 20 = 18 pages
for (i in 1:18){

  url = paste0("https://slate.com/tag/government-shutdown/", i)

  remDr$navigate(url)

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))

  #find the urls for page X
  webElems <- remDr$findElements(using = "css", "[href]")

  #add the urls to a list
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))

  #don't go too fast
  Sys.sleep(runif(1, 1, 5))
}

remDr$close()
# stop the selenium server
rD[["server"]]$stop()

beep(sound = 3)

##deal with the URLS
urlslist = unlist(urlslist_final)

#find all the ones with /2018/
urlslist2.1 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
urlslist2.1 = unique(urlslist2.1)

urlslist3 = unique(c(urlslist2, urlslist2.1))

##start a data frame
SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
colnames(SLATEDF) = c("Source", "Url", "Text")
SLATEDF = as.data.frame(SLATEDF)

##for loops
for (i in 1:length(urlslist3)){

  ##read in the URL
  webpage2 <- read_html(urlslist3[i])

  ##pull the specific nodes
  headline_data2 = html_nodes(webpage2,'.slate-paragraph')

  ##pull the text
  text_data2 = html_text(headline_data2)

  ##save the data
  SLATEDF$Source[i] = "SLATE"
  SLATEDF$Url[i] = urlslist3[i]
  SLATEDF$Text[i] = paste(text_data2, collapse = "")
  Sys.sleep(runif(1, 1, 10))
} ##end for loop

#beep(sound = 3)

write.csv(SLATEDF, "SLATE_gs.csv", row.names = F)
```

```{r HuffPo_kav, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)
library(lubridate)

#open the browser
rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
remDr <- rD[["client"]]

url = "https://search.huffpost.com/search?utf8=%E2%9C%93&p=kavanaugh&fr=huffpost_desktop-s"

remDr$navigate(url)

#create a blank space to put the links
urlslist_final = list()

#loop over the results and go through them
#943 results with 10 per page 94 clicks
for (i in 1:94){

  #find the urls for page X
  webElems <- remDr$findElements(using = "class name", "fz-20")

>>>>

```{r load_packages, include = FALSE}
library(papaja) 
library(MuMIn)
library(reshape)
library(nlme)
library(ggplot2)
library(expss)
library(MOTE)
library(quanteda)
library(quanteda.textstats)
library(tm)
library(ngram)
library(ggplot2)
library(reshape)
library(knitr)

@@

```{r include = F, eval = F}
# to see the web scraping and data cleanup for this section see web_scraping.Rmd
# this code was run previously to create the data for this manuscript
# note that website changes to places like the NYT means it likely does
# not run in the same way anymore 
```

@@

@@

```{r stem_text, eval=TRUE, include=FALSE}
final = read.csv("../exp1_data/finaldata.csv", stringsAsFactors = F)
final = na.omit(final) #one weird NA line

@@

```{r exp1_descriptive_calc, echo = F, include = F}
final$uniquewords = NA
final$valenceavg = NA

@@

tableprint = tableprint[c(3, 4, 1, 2) , ]
```

```{r exp1-source-descriptives, results = 'asis', echo = FALSE}
#change this to match
apa_table(as.data.frame(tableprint),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula. V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
          caption = "Experiment 1 - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 10)), 
          font_size = 'footnotesize'
          )
```

@@

```{r exp1_table_calc, include = F, echo = F}
#MFD, mean, sd, mean, sd, t, p, d
tableprint2 = matrix(NA, ncol = 8, nrow = 5)
colnames(tableprint2) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")

@@

#put in the numbers
tableprint2[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                    harm_d$d)
tableprint2[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1, 
                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
                    fair_d$d)
tableprint2[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1, 
                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
                    ingroup_d$d)
tableprint2[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1, 
                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
                    authority_d$d)
tableprint2[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1, 
                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
                    purity_d$d)

tableprint2[ , c(2:6, 8)] = printnum(as.numeric(tableprint2[ , c(2:6, 8)]))
tableprint2[ , 7] = printp(as.numeric(tableprint2[ , 7]))
```

```{r exp1-table, results = 'asis', echo = F}
apa_table(as.data.frame(tableprint2),
          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
          caption = "Experiment 1 Results - Multilevel Model",
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7)),
          font_size = 'footnotesize'
          )
```

@@

```{r include = F, echo = F}
# please see the web_scraping.Rmd to see how we originally collected this data
```
